Canonical rings of rational divisors on projective space and Hirzebruch surfaces

### 2015-07-14 surfaces-write-up/surface-write-up.tex
manually undo peter's silly push

\begin{prop}
\label{prop:cone-generation}
Let $n,t \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$ and let $k_i^j \in \bz$ with $1 \leq i \leq n, 1 \leq j \leq t.$ Define
\begin{align*}
	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}
\end{align*}
Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_r$.  Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\pdeg_i$. Furthermore, every element $\sigma \in \Sigma$ can be written in a canonical form $\lambda + \sum_{i=1}^{t} w_i e_i,$ with the first coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$ and $w_1,\ldots, w_t \in \bz$.

>>>>

\begin{prop}
\label{prop:cone-generation}
Let $n,t \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$ and let $k_i^j \in \bz$ with $1 \leq i \leq n, 1 \leq j \leq t.$ Define
\begin{align*}
	\Sigma = \{(d, c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}
\end{align*}

\noindent
Let $e_1, \ldots, e_t \in \Sigma,$ with $e_i = (\pdeg_i, c_1^i,
\ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$,
meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of
$e_1, \ldots, e_t$.  Then, as a semigroup, $\Sigma$ is generated by
elements whose first coordinate is less than $\sum_{i = 1}^{n} \pdeg_i$
. Furthermore, every element $\sigma \in \Sigma$ can be written in
a canonical form $\lambda + \sum_{i=1}^{t} w_i e_i,$ with the first
coordinate of $\lambda$ less than $\sum_{i=1}^{t}\pdeg_i$ and $w_1,
\ldots, w_t \in \bz$.
